Democratizing MPC

### 2017-10-06 OaklandSubmission/intro.tex
intro

Secure multiparty computation \cite{yao,gmw} (SMC) is a powerful cryptographic tool that allows a set of mutually distrusting parties to compute a joint function of their secret inputs. Examples of these include various machine learning prediction algorithm where one party holds the secret input such as a medical report and the other party holds the ML model for disease prediction. Since the introduction of SMC in 1980's, there has been a large body of work \cite{..} that has transformed SMC from a mere theoretical tool to something practically efficient/usable.

Unfortunately, implementing functionalities using SMC protocols requires thorough understanding of cryptography. To allow for widespread use of SMC, it is critical that SMC protocols are programmable by non-cryptographic experts. To cater to this, there have been several efforts developing domain-specific languages that are programmer friendly and compile to a SMC back-end. Most notable of these domain specific languages and systems include \cite{...}. All of these works build on a cryptographic back-end that is either entirely boolean \cite{yao,gmw} or arithmetic \cite{homo}. In fact, most of these works use boolean circuits based scheme for completeness. However, most interesting functions require a mix of arithmetic and boolean computations.  Examples include ......... As one can expect, expressing these computations as boolean circuits is one of the biggest efficiency bottleneck. \divya{Note that comparisons cannot be expressed in arithmetic circuits}

To address this issue, recently Demmler et al. \cite{aby} gave a framework for SMC where the parties can mix arithmetic and boolean computations and demonstrated great performance benefits \divya{on small examples}. However, using their system requires the programmer to be aware of trade-offs of arithmetic and boolean cryptographic schemes. The programmer writes circuits consisting of a mix of arithmetic and boolean gates along with appropriate conversion gates. In short, as is also mentioned by the authors themselves, \cite{aby} is not suitable to be used by non-specialist programmers.

@@

In this work, we develop and implement our framework \tool where the programmer writes a high level C-like program (instead of a circuit) to describe the function to be computed. Our compiler automatically converts this program to a suitable SMC protocol that uses both arithmetic and boolean secure computation components. Our framework can work with any secure implementation of a mix of arithmetic and boolean computations. In our work, we focus on semi-honest secure two-party computation and  ABY \cite{aby} provides the suitable cryptographic back-end. \divya{We provide a formal type system.... } We evaluate our system on benchmarks from \cite{} and show that automatically generated protocols match the performance of hand-crafted protocols in most cases (see \ref{sec:eval}). \divya{Below, we will  give an overview of \tool and describe our contributions.}

@@

\divya{ideally have small paragraphs about key features}
1. ease to programming.. refer to section with example in our language; contrast to verilog paper; programmer is completely oblivious of security; looks like a normal C program

>>>>

Most cryptographic tools rely on circuit as abstractions for any general computation but real-life developers write programs. It is critical to address this fundamental  representation gap to make cryptography accessible to non-crypto specialist developers. In this work, we address this gap for the case of secure multi-party computation.

Secure multi-party computation \cite{yao,gmw} (SMC) is a powerful cryptographic tool that allows a set of mutually distrusting parties to compute a joint function of their secret inputs. Examples of these include various machine learning prediction algorithm where one party holds the secret input such as a medical report and the other party holds the ML model for disease prediction. Since the introduction of SMC in 1980's, there has been a large body of work \cite{..} that has transformed SMC from a mere theoretical tool to something practically efficient/usable.

Unfortunately, implementing functionalities using SMC protocols requires thorough understanding of cryptography. To allow for widespread use of SMC, it is critical that SMC protocols are programmable by non-cryptographic experts. To cater to this, there have been several efforts developing domain-specific languages that are programmer friendly and compile to a SMC protocol. Most notable of these domain specific languages and systems include \cite{...}. All of these works build on a cryptographic back-end that is either entirely boolean \cite{yao,gmw} or arithmetic \cite{homo}. In fact, most of these works use boolean circuits based scheme for completeness\footnote{Note that comparisons cannot be expressed in arithmetic circuits}. However, most interesting functions require a mix of arithmetic and boolean computations.  Examples include ......... As one can expect, compiling these programs to boolean circuits is one of the biggest efficiency bottlenecks. \divya{Our work addresses this performance bottleneck.}

To address this issue \divya{on the cryptographic side}, recently Demmler et al. \cite{aby} gave a cryptographic protocol for SMC where the parties can mix arithmetic and boolean computations and claimed potentially great performance benefits. However, using their system requires the programmer to be aware of trade-offs of arithmetic and boolean cryptographic schemes. In their framework, the programmer is required to write circuits consisting of a mix of arithmetic and boolean gates along with appropriate conversion gates. In short, as is also mentioned by the authors themselves, the current system is not suitable to be used by non-specialist programmers.

@@

In this work, we develop and implement our framework \tool where the programmer writes a high level C-like program (instead of a circuit) to describe the function to be computed. Our compiler automatically converts this program to a suitable SMC protocol that uses both arithmetic and boolean secure computation components as well as the correct conversion protocols whenever required. Our compiler is general and can work with any secure implementation of a mix of arithmetic and boolean computations. In our work, we focus on semi-honest secure two-party computation and  ABY \cite{aby} provides the suitable cryptographic back-end. \divya{We provide a formal type system.... } We evaluate our system on various benchmarks from \cite{} and show that automatically generated protocols match the performance of hand-crafted protocols in most cases (see \ref{sec:eval}). \divya{Below, we will  give an overview of \tool and describe our contributions.}

@@

\divya{ideally have small paragraphs about key features}
1. ease to programming.. refer to section with example in our language; contrast to verilog paper; programmer is completely oblivious of security; looks like a normal C program;
also say that user does not write keywords secret and public; these are inferred from the information flow
